HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-17 paper/main.tex
sss

We proceed to detailing how judgements on the semantic units
of the source are aggregated into a composite score.
While future extensive empirical evaluation with HUME and its application to MT
system tuning may suggest more complex definition,
as a starting point we take a parsimonious approach
and simply aggregate the judgements.

@@

\vspace{-.5cm}
\begin{equation}
  \small
  \HUME(s,t) = \frac{\Correct(s,t) + 0.5\cdot \Partial(s,t)}{\setsize{\Units(s)}}
\end{equation}

@@

We turn to discuss the interface for collecting human judgements on the semantic units
of the source, relating to the translation. UCCA annotations of the source are done offline,
using the UCCA web application\footnote{See UCCA webpage.}.

@@

The interface presents, for each unit, the translation segment aligned with it.
This allows the user, especially in long sentences, to focus her attention on the parts
most likely to be relevant for her judgement. As the alignments are automatically derived,
and therefore noisy, the annotator is instructed to treat the aligned text is a cue, but to ignore
it and make a judgement according to the full translation sentence, in cases where the alignment
is misleading.

Concretely, let $s = (w_1,\ldots,w_n)$ be a source sentence, $t = (w'_1,\ldots,w'_n)$ a translation,
and $A \subset 2^{s \times t}$ a many-to-many word alignment between them.
If $u$ is a semantic unit in $s$, whose yield is $yld(u)$, we define the aligned text in
$t$ to be $a(u)=\bigcup_{(x_s,x_t) \in A \wedge x_s \cap yld(u) \neq \emptyset} x_t \subset t$.
In the event that $a(u)$ is discontiguous in the text, words between the left
and right boundaries of $a(u)$ which are not contained in it (intervening words)
are presented in a smaller red font.
Intervening words are likely change the meaning of the translation
of $u$, and thus should be paid attention to when considering whether the translation
is correct or not.

For example, consider the sentence $s=$``The man watched the dog'' and the German
translation ``t=Der Mann sieht den Hund an''. Then ``watched'' will be aligned to
``sieht ... an'', and ``den Hund'' will be marked as intervening word. Another example
can be seen in \figref{fig:interface}, where ``ongoing pregnancy'' is translated to
``Schwangerschaft ... laufenden'' (lit. ``pregnancy ... ongoing'').

>>>>

We proceed to detailing how judgements on the semantic units
of the source are aggregated into a composite score.
While future extensive empirical evaluation with HUME and its application to MT
system tuning may suggest more complex definition,
as a starting point we take a parsimonious approach,
and compute an accuracy score.

@@

\vspace{-.5cm}
\begin{equation}
  \small
  \HUME(s,t) = \frac{\Correct(s,t) + 0.5\cdot \Partial(s,t)}{\setsize{\Units(s)}}
  \nonumber
\end{equation}

@@

We turn to discuss the interface for collecting human judgements on the semantic units
of the source, relating to the translation. UCCA annotations of the source are done offline,
using the UCCA web application.

@@

The interface presents, for each unit, the translation segment aligned with it.
This allows the user, especially in long sentences, to focus her attention on the parts
most likely to be relevant for her judgement. As the alignments are automatically derived,
and therefore noisy, the annotator is instructed to treat the aligned text is a cue, but to ignore
the alignment if it is misleading, and instead 
make a judgement according to the full translation sentence.

Concretely, let $s = (w_1,\ldots,w_n)$ be a source sentence, $t = (w'_1,\ldots,w'_n)$ a translation,
and $A \subset 2^{s \times t}$ a many-to-many word alignment between them.
If $u$ is a semantic unit in $s$, whose yield is $yld(u)$, we define the aligned text in
$t$ to be $a(u)=\bigcup_{(x_s,x_t) \in A \wedge x_s \cap yld(u) \neq \emptyset} x_t \subset t$.
Where $a(u)$ is discontiguous in the text, words between the left
and right boundaries of $a(u)$ which are not contained in it (intervening words)
are presented in a smaller red font.
Intervening words are likely change the meaning of the translation
of $u$, and thus should be paid attention to when considering whether the translation
is correct or not.

For example, consider the sentence $s=$``We're driving back on Friday'' and the German
translation t=``Am Freitag fahren wir zur\"uck'' (lit. ``on Friday driving we back'').
``driving back'' will be aligned to ``fahren ... zur\"uck'',
and ``wir'' will be marked as intervening word. Another example
appears in \figref{fig:interface}, where ``ongoing pregnancy'' is translated to
``Schwangerschaft ... laufenden'' (lit. ``pregnancy ... ongoing'').
